\papertitle

### 2014-03-21 final-report/paper.tex
m

\todo{is this figure necessary or is the figure in the evaluation section enough?}

@@

When the user clicks on a matrix cell, they are able to view the breakdown of the worker pair communication in a
time series chart below the matrix. The user can select multiple such cells to compare different time
series. Figure~\ref{fig:ts} shows an example when the user selected two pairs: (8-2) and (7-6). The x-axis shows
time in seconds and y-axis shows number of tuples exchanged between the source and destination workers.
Just looking at the matrix chart it is evident that there is more data exchanged between the source-destination pair
(8-2) than the pair (7-6). But as the time series comparison shows, there is more communication between (7-6)
than (8-2) for the last 2.5 seconds of the query execution. This points to interesting patterns as to the rate at which
work is done at different workers at different stages of the execution. Distinct points on the lines are highlighted as
black dots. Hovering the cursor over a dot shows the information for that data point in a tooltip. Meanwhile the cells
in the matrix remain highlighted with the same color used to draw the corresponding time series line. This aids in the
user keeping track of the mapping between the matrix cell and the corresponding time series line. We also provide
a 'clear selection' button that erases everything from the time series chart upon clicking. Finally we provide the
functionality whereby clicking a row or column label selects every cell in that row or column and displays the
corresponding time series in the time series chart.

>>>>

%\todo{is this figure necessary or is the figure in the evaluation section enough?}

@@

When the user clicks on a matrix cell, they are able to view the breakdown of the worker pair communication in a
time series chart below the matrix. The user can select multiple such cells to compare different time
series. Figure~\ref{fig:ts} shows an example when the user selected two pairs: (8-1) and (7-5). The x-axis shows
time in seconds and y-axis shows number of tuples exchanged between the source and destination workers.
Just looking at the matrix chart it is evident that there is more data exchanged between the source-destination pair
(8-2) than the pair (7-6). But as the time series comparison shows, there is more communication between (7-5)
than (8-1) for the last 2.5 seconds of the query execution. This points to interesting patterns as to the rate at which
work is done at different workers at different stages of the execution. Distinct points on the lines are highlighted as
black dots. Hovering the cursor over a dot shows the information for that data point in a tooltip. Meanwhile the cells
in the matrix remain highlighted with the same color used to draw the corresponding time series line. This aids in the
user keeping track of the mapping between the matrix cell and the corresponding time series line. We also provide
a 'clear selection' button that erases everything from the time series chart upon clicking. Finally we provide the
functionality whereby clicking a row or column label selects every cell in that row or column and displays the
corresponding time series in the time series chart.
